\textsc{Rils}-\textsc{Rols} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-11-11 paper_resources/doc/paper.tex
Update: conclusion

\textsc{Rils-Rols} method is compared to the 14 other competitor algorithms from the literature on the two ground truth benchmark sets from literature, namely \textsc{Feynman} and \textsc{Strogatz}.  Additionally, we introduced a non-biased benchmark set of randomly generated instances, labelled by \textsc{Random}.  The experimental evaluation confirmed the efficiency of our method which produced the best average ranking results in terms of exact percentage when compared to all other competitors on the two ground-truth benchmarks in the presence of all three different levels of noise in the input data. In all cases, new best exact percentages are obtained using \textsc{Rils-Rols} method.  
Moreover, the scalability and robustness of this method are checked and confirmed on the unbiased \textsc{Random} benchmark set in terms of a few different criteria such as the size of the model, the number of variables included in exact models, and obtained average runtimes.

>>>>

\textsc{Rils-Rols} method is compared to the 14 other competitor algorithms from the literature on the two ground truth benchmark sets from literature, namely \textsc{Feynman} and \textsc{Strogatz}.  Additionally, we introduced a non-biased benchmark set of randomly generated instances, labelled by \textsc{Random}.  The experimental evaluation confirmed the efficiency of our method which produced the best average ranking results in terms of exact percentage when compared to all other competitors on the two ground-truth benchmarks in the presence of all three different levels of noise in the input data. In all cases, new best exact percentages are obtained using \textsc{Rils-Rols} method.   More in details,
our algorithm was able to obtain the right model on 60.62\%, 42.08\%, and 34.77\% problem instances in the presence of the noise level of 0.0, 0.001, and 0.01, respectively. Just for the shake of comparisons, the second best approach \textsc{AI-Feynman}, when the noise level of 0.0 and 0.001 is included, obtained an exact percentage rate of 52.65\%, and 31.89\%, respectively. In case of the highest noise level, the second best approach was \textsc{Afp-Fe}, obtaining an exact percentage rate of 20\%. Additionally, the scalability and robustness of this method are checked and confirmed on the unbiased \textsc{Random} benchmark set in terms of a few different criteria such as the size of the model, the number of variables included in exact models, and obtained average runtimes.
